---
title: "time_course_multimid"
author: "Ryan Yan"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("load_libraries.R"))
```

```{r}
purpleOrange_palette6 = c("purple4","purple2","plum3","gold","orange","goldenrod")
purpleOrange_palette3 = c("purple4","plum3","orange")
purpleOrange_palette2 = c("purple4","orange")

```

```{r}
data_dir <- "/Users/rh/Desktop/evalscal/multimid/"
tc_multimid <- read_csv(paste0(data_dir,"timecourses_N18_long_woOutlier.csv"))

unique(tc_multimid$cue_value)

tc_multimid <- tc_multimid%>%
  mutate(cue_value = if_else(cue_value == "($1)", "-$1", 
                             if_else(cue_value == "($5)","-$5", 
                                     if_else(cue_value %in% c("$0","$1","$5"),paste0("+",cue_value),cue_value))),
         trial_gain = if_else(trial_gain == "($1)", "-$1", 
                             if_else(trial_gain == "($5)","-$5", 
                                     if_else(trial_gain %in% c("$0","$1","$5"),paste0("+",trial_gain),trial_gain))))
tc_multimid$cue_value <- factor(tc_multimid$cue_value, levels = c( "-$5","-$1","-$0","+$0","+$1","+$5"))
tc_multimid$trial_gain <- factor(tc_multimid$trial_gain, levels = c( "-$5","-$1","-$0","+$0","+$1","+$5"))
```

```{r}
vois <- c("nacc","mpfc","anteriorinsula","anteriorcingulate","v1","wm")

tc_multimid_mb1 <- tc_multimid%>%
  filter(mb == 1, voi %in% vois)

tc_multimid_mb1$voi <- factor(tc_multimid_mb1$voi,level = vois)
```

```{r}
head(tc_multimid_mb1)
subj <- unique(tc_multimid_mb1$subject)

tc_multimid_mb1 <- tc_multimid_mb1%>%
  rowwise()%>%
  mutate(cue_value_num = as.numeric(paste0(strsplit(as.character(cue_value),"")[[1]][1],
                                strsplit(as.character(cue_value),"")[[1]][3])),
         trial_gain_num = if_else(hit == 1 & cue_value_num >= 0, cue_value_num, 
                                  if_else(hit == 1 & cue_value_num < 0, 0,
                                          if_else(hit == 0 & cue_value_num >= 0, 0,
                                                  if_else(hit == 0 & cue_value_num < 0, cue_value_num, -99)))))

## get recent rolling mean
tc_multimid_mb1 <- tc_multimid_mb1%>%
  group_by(subject,voi,tr)%>%
  mutate(last_iti = as.factor(lag(iti,1)),
         last_hit = lag(hit,1),
         last_cue = lag(cue_value,1),
         last_gain = lag(trial_gain,1),
         last_gain_num = lag(trial_gain_num,1),
         recent_avg_gain = lag(rollmean(trial_gain_num, 10,fill = c(0,0,0), align = "right"),1),
         prediction_error_approx = trial_gain_num - recent_avg_gain,
         gain_contrast = trial_gain_num - last_gain_num,
         recent_avg_winpercent = lag(rollmean(hit, 10, na.pad = TRUE, align = "right"),1)
         )

#check rolling winpercent
ggplot(tc_multimid_mb1%>%
         filter(voi == "mpfc", subject == subj[1]), aes(x = trial))+
  geom_point(aes(y = hit, color = hit))+
  geom_line(aes(y = recent_avg_winpercent),color = "red")

#check rolling mean
ggplot(tc_multimid_mb1%>%
         filter(voi == "mpfc", subject == subj[1]), aes(x = trial))+
  geom_line(aes(y = recent_avg_gain),color = "red")+
  geom_line(aes(y = trial_gain_num),linetype = "dashed")+
  geom_line(aes(y = prediction_error_approx), color = "orange",size = 2)

tc_multimid_mb1$recent_avg_winpercent[is.na(tc_multimid_mb1$recent_avg_winpercent)] <- tc_multimid_mb1$total_winpercent[is.na(tc_multimid_mb1$recent_avg_winpercent)]
tc_multimid_mb1$last_iti <- as.factor(tc_multimid_mb1$last_iti)
```

## behavioral analysis
```{r message = FALSE, echo = TRUE}
# this function shifts the lower bound of the y axis around in a ggplot
shift_trans = function(d = 0) {
  scales::trans_new("shift", transform = function(x) x - d, inverse = function(x) x + d)
}
```

```{r}
mid_beh <- unique(tc_multimid_mb1%>%
                    ungroup()%>%
  dplyr::select(-voi:-time))

ggplot(mid_beh%>%
         group_by(cue_value)%>%
         summarise(hit_rate = mean(hit),
                   hit_rate_se = sd(hit)/length(subj)), aes(x = cue_value, y = hit_rate, fill = cue_value))+
  geom_col()+
  geom_errorbar(aes(ymin = hit_rate - hit_rate_se, ymax = hit_rate + hit_rate_se),width = 0.2)+
  scale_fill_manual(values = purpleOrange_palette6)+
  scale_y_continuous(trans = shift_trans(0.3),limits = c(NA, 0.75))

table(mid_beh%>%
      dplyr::select(trial_gain,cue_value))

ggplot(mid_beh%>%
         group_by(cue_value,iti)%>%
         summarise(hit_rate = mean(hit),
                   hit_rate_se = sd(hit)/length(subj)), aes(x = iti, y = hit_rate, fill = cue_value))+
  geom_col()+
  facet_wrap(~cue_value)+
  geom_errorbar(aes(ymin = hit_rate - hit_rate_se, ymax = hit_rate + hit_rate_se),width = 0.2)+
  scale_fill_manual(values = purpleOrange_palette6)+
  scale_y_continuous(trans = shift_trans(0.3),limits = c(NA, 0.75))
```

```{r}
cor_mat <- cor(mid_beh%>%
  ungroup()%>%
  dplyr::select(trial_gain_num,recent_avg_gain,prediction_error_approx,recent_avg_winpercent), use = "complete.obs")

p_mat <- cor_pmat(mid_beh%>%
  ungroup()%>%
  dplyr::select(trial_gain_num,recent_avg_gain,prediction_error_approx,recent_avg_winpercent))

ggcorrplot.mixed(cor_mat, lower = "number",upper = "ellipse", p.mat = p_mat, insig = "label_sig")
```

#voi analysis

```{r}
# cue-locked
tc_multimid_mb1$tr <- as.factor(tc_multimid_mb1$tr)

ggplot(tc_multimid_mb1,aes(x = time, y = BOLD, color = cue_value))+
  stat_summary(aes(group = cue_value),geom = "line",size=1)+
  stat_summary(geom = "pointrange",size=0.5)+
  facet_wrap(~voi)+
  scale_color_manual(values = purpleOrange_palette6)+
  annotate("rect", xmin = 6, xmax = 8, ymin = -0.25, ymax = 0.4, 
           alpha = .2)

# lm1 <- lmer(BOLD ~ cue_value * as.factor(tr) * voi + (voi|subject),tc_multimid_mb1)
# plot_model(lm1,type = "pred",terms = c("tr","cue_value","voi"),colors = purpleOrange_palette6)+
#   theme_bw()+
#   annotate("rect", xmin = 4, xmax = 6, ymin = -0.25, ymax = 0.4, 
#            alpha = .2)
```

## by cue value
```{r}
lm_ant_nacc <- lmer(BOLD ~ cue_value + (1|subject),tc_multimid_mb1%>%
       filter(voi == "nacc", tr == 4))
summary(lm_ant_nacc)
plot_model(lm_ant_nacc,type = "pred", terms = c("cue_value"))

lm_ant_ains <- lmer(BOLD ~ cue_value + (1|subject),tc_multimid_mb1%>%
       filter(voi == "anteriorinsula", tr == 4))
summary(lm_ant_ains)
plot_model(lm_ant_ains,type = "pred", terms = c("cue_value"))
```

## by hit or miss
```{r}
# cue-locked
ggplot(tc_multimid_mb1,aes(x = time, y = BOLD, color = as.factor(hit)))+
  stat_summary(geom = "line",size=1)+
  stat_summary(geom = "pointrange",size=0.5)+
  facet_wrap(~voi)+
  scale_color_manual(values = purpleOrange_palette2)+
  annotate("rect", xmin = 12, xmax = 14, ymin = -0.25, ymax = 0.4, 
           alpha = .2)+
  labs(title = "hit vs. miss")

lm_hit <- lmer(BOLD ~ hit + (1|subject),tc_multimid_mb1%>%
       filter(voi == "mpfc", tr == 7))
summary(lm_hit)
```


## by outcome value
```{r warning = FALSE, message = FALSE, fig.width=6,fig.height=8}
# cue-locked
ggplot(tc_multimid_mb1,aes(x = time, y = BOLD, group = hit, color = cue_value))+
  stat_summary(geom = "line",size=1, aes(linetype = if_else(tc_multimid_mb1$hit == 1, "solid","dashed")))+
  stat_summary(geom = "pointrange",size=0.5)+
  facet_wrap(~cue_value+voi)+
  scale_color_manual(values = purpleOrange_palette6)+
  annotate("rect", xmin = 12, xmax = 14, ymin = -0.25, ymax = 0.4, 
           alpha = .2)+
  annotate("rect", xmin = 6, xmax = 8, ymin = -0.25, ymax = 0.4, 
           alpha = .2, fill = "steelblue")
```

```{r}
## trial_gain does not work because +$0 has multiple meanings
lm_gain <- lmer(BOLD ~ trial_gain + (1|subject),tc_multimid_mb1%>%
       filter(voi == "mpfc", tr == 7))
summary(lm_gain)

lm_gain_by_cue <- lmer(BOLD ~ cue_value * hit + (1|subject),tc_multimid_mb1%>%
       filter(voi == "mpfc", tr == 7))
summary(lm_gain_by_cue)
plot_model(lm_gain_by_cue, type = "pred",terms = c("cue_value","hit"))

plot_model(lmer(BOLD ~ trial_gain + (1|subject),tc_multimid_mb1%>%
       filter(voi == "mpfc", tr == 7)), type = "pred",terms = c("trial_gain"))

ggplot(tc_multimid_mb1%>%filter(cue_value == "+$5"),aes(x = time, y = BOLD, color = as.factor(hit)))+
  stat_summary(geom = "line",size=1)+
  stat_summary(geom = "pointrange",size=0.5)+
  facet_wrap(~voi)+
  scale_color_manual(values = purpleOrange_palette2)+
  annotate("rect", xmin = 12, xmax = 14, ymin = -0.25, ymax = 0.4, 
           alpha = .2)+
  labs(title = "+$5 gain vs. no-gain")

ggplot(tc_multimid_mb1%>%filter(cue_value == "+$1"),aes(x = time, y = BOLD, color = as.factor(hit)))+
  stat_summary(geom = "line",size=1)+
  stat_summary(geom = "pointrange",size=0.5)+
  facet_wrap(~voi)+
  scale_color_manual(values = purpleOrange_palette2)+
  annotate("rect", xmin = 12, xmax = 14, ymin = -0.25, ymax = 0.4, 
           alpha = .2)+
  labs(title = "+$1 gain vs. no-gain")
```

# functional form of anticipatory signal
```{r}
voi_form <- tc_multimid_mb1%>%
       filter(tr == 4)%>%
  group_by(voi,subject,cue_value)%>%
  summarise(BOLD = mean(BOLD,na.rm = TRUE))
voi_form$cue_value <- factor(voi_form$cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

ggplot(voi_form,
       aes(x = cue_value, y = BOLD))+
  facet_wrap(~voi)+
  geom_point(alpha=0.3)+
  geom_line(aes(group = subject))+
  stat_summary(geom = "pointrange", color = "red")
```


# context-modulated anticopatory activity
```{r}
df_lm_ant <- tc_multimid_mb1%>%
  dplyr::select(trial, hit, tr,time, cue_value, cue_value_num, voi, BOLD,recent_avg_gain,trial_gain, prediction_error_approx,recent_avg_winpercent,drift,last_gain,gain_contrast,last_iti)%>%
  filter(tr == 4)
df_lm_ant$trial_gain <- factor(df_lm_ant$trial_gain, levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))
df_lm_ant$cue_value <- factor(df_lm_ant$cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

df_lm_ant$recent_avg_winpercent <- as.numeric(df_lm_ant$recent_avg_winpercent)

```

## nacc
```{r}
lm_nacc_1 <- lmer(BOLD ~ cue_value + (1|subject),df_lm_ant%>%filter(voi == "nacc"))

plot_model(lm_nacc_1, type = "pred", terms = c("cue_value"),colors = purpleOrange_palette2)+
  geom_line()

lm_nacc_2 <- lmer(BOLD ~ cue_value * recent_avg_winpercent  + (1|subject),df_lm_ant%>%filter(voi == "nacc"))

plot_model(lm_nacc_2, type = "pred", terms = c("cue_value","recent_avg_winpercent[0,0.5,1]"),colors = purpleOrange_palette3)+
  geom_line()

summary(lm_nacc_2)

lm_nacc_3 <- lmer(BOLD ~ recent_avg_winpercent +(1|subject),df_lm_ant%>%filter(voi == "nacc", cue_value == "+$5"))
# + last_gain
summary(lm_nacc_3)

plot_model(lm_nacc_3, type = "pred", terms = c("recent_avg_winpercent"))+
  geom_vline(xintercept = 0.66, linetype = "dashed")+
  labs(title = "B = -0.4481, p = .005")
```




## ains (none)
```{r}
lm_ains_1 <- lmer(BOLD ~ cue_value + (1|subject),df_lm_ant%>%filter(voi == "anteriorinsula"))

plot_model(lm_ains_1, type = "pred", terms = c("cue_value"),colors = purpleOrange_palette2)+
  geom_line()

lm_ains_2 <- lmer(BOLD ~ cue_value * recent_avg_winpercent  + (1|subject),df_lm_ant%>%filter(voi == "anteriorinsula"))

plot_model(lm_ains_2, type = "pred", terms = c("cue_value","recent_avg_winpercent[0,0.5,1]"),colors = purpleOrange_palette3)+
  geom_line()

summary(lm_ains_2)

lm_ains_3 <- lmer(BOLD ~ recent_avg_winpercent + drift +(1|subject),df_lm_ant%>%filter(voi == "anteriorinsula", cue_value == "+$5"))

summary(lm_ains_3)

plot_model(lm_ains_3, type = "pred", terms = c("recent_avg_winpercent"))
```

# context-modulated outcome activity
```{r}
df_lm_out <- tc_multimid_mb1%>%
  dplyr::select(trial, hit, tr,time, cue_value, cue_value_num, voi, BOLD,recent_avg_gain,trial_gain, prediction_error_approx,recent_avg_winpercent,drift, last_gain, gain_contrast)%>%
  filter(tr == 7)
df_lm_out$trial_gain <- factor(df_lm_out$trial_gain, levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))
df_lm_out$cue_value <- factor(df_lm_out$cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

df_lm_out$recent_avg_winpercent <- as.numeric(df_lm_out$recent_avg_winpercent)
```

## mpfc
```{r}
lm_mpfc_1 <- lmer(BOLD ~ cue_value * hit + (1|subject),df_lm_out%>%filter(voi == "mpfc"))

plot_model(lm_mpfc_1, type = "pred", terms = c("cue_value","hit"),colors = purpleOrange_palette2)+
  geom_line()

lm_mpfc_2 <- lmer(BOLD ~ cue_value * hit * recent_avg_winpercent  + (1|subject),df_lm_out%>%filter(voi == "mpfc"))

plot_model(lm_mpfc_2, type = "pred", terms = c("cue_value","recent_avg_winpercent[0,0.5,1]","hit"),colors = purpleOrange_palette3)+
  geom_line()

lm_mpfc_3 <- lmer(BOLD ~  recent_avg_winpercent * hit + (1|subject),df_lm_out%>%filter(voi == "mpfc", cue_value == "+$5"))

plot_model(lm_mpfc_3, type = "pred", terms = c("recent_avg_winpercent","hit"),colors = purpleOrange_palette2)+
  geom_line()+
  geom_vline(xintercept = 0.66, linetype = "dashed")+
  labs(title = "B = -0.52, p = .051")

summary(lm_mpfc_3)

lm_mpfc_4 <- lmer(BOLD ~  hit * last_gain + (1|subject),df_lm_out%>%filter(voi == "mpfc", cue_value == "+$5"))

plot_model(lm_mpfc_4, type = "pred", terms = c("last_gain","hit"),colors = purpleOrange_palette2)+
  geom_line()+
  geom_vline(xintercept = 0.66, linetype = "dashed")+
  geom_hline(yintercept = 0, linetype = "dashed")
```

### Prediction error
```{r}
lm_mpfc_4 <- lmer(BOLD ~ scale(prediction_error_approx) + (1|subject),df_lm_out%>%filter(voi == "mpfc", cue_value == "+$5"))
summary(lm_mpfc_4)

plot_model(lm_mpfc_4, type = "pred", terms = c("prediction_error_approx"),colors = purpleOrange_palette3)+
  geom_line()+
  geom_vline(xintercept = 5, linetype = "dashed")+
  geom_hline(yintercept = 0, linetype = "dashed")+
  labs(title = "B = 0.14, p < .001")


lm_mpfc_5 <- lmer(BOLD ~ prediction_error_approx + recent_avg_winpercent + recent_avg_gain + (1|subject),df_lm_out%>%filter(voi == "mpfc", cue_value == "+$5"))
summary(lm_mpfc_5)

plot_model(lm_mpfc_5, type = "pred", terms = c("prediction_error_approx"),colors = purpleOrange_palette3)+
  geom_line()+
  geom_vline(xintercept = 5, linetype = "dashed")+
  geom_hline(yintercept = 0, linetype = "dashed")

plot_model(lm_mpfc_5, type = "pred", terms = c("recent_avg_winpercent"),colors = purpleOrange_palette3)+
  geom_line()
```

### gain contrast (similar to PE)
```{r}
lm_mpfc_6 <- lmer(BOLD ~ gain_contrast + (1|subject),df_lm_out%>%filter(voi == "mpfc", cue_value == "+$5"))
summary(lm_mpfc_6)
```

## wm
```{r}
lm_wm_1 <- lmer(BOLD ~ cue_value * hit + (1|subject),df_lm_out%>%filter(voi == "wm"))

plot_model(lm_wm_1, type = "pred", terms = c("cue_value","hit"),colors = purpleOrange_palette2)+
  geom_line()

lm_wm_2 <- lmer(BOLD ~  recent_avg_winpercent + (1|subject),df_lm_out%>%filter(voi == "wm", cue_value == "+$5", hit == 1))

plot_model(lm_wm_2, type = "pred", terms = c("recent_avg_winpercent"),colors = purpleOrange_palette3)+
  geom_line()

summary(lm_wm_2)
```

# effect of last trial on this trial
## ITI
### iti range
```{r}
iti_mod_lm <- lmer(BOLD ~ as.factor(time) * as.factor(hit) * cue_value + (1|subject),tc_multimid_mb1%>%filter(voi == "nacc"))
plot_model(iti_mod_lm, type = "pred", terms = c("time","hit","cue_value"),colors = purpleOrange_palette2)+
  geom_hline(yintercept = 0)+
  annotate("rect", xmin = 10, xmax = 18, ymin = -0.4, ymax = 0.4, 
           alpha = .2)+
  geom_vline(xintercept = c(10,12,14), linetype = "dashed")+
  labs(title = "Nacc")
```

```{r}
nacc_iti_mod <- tc_multimid_mb1%>%
  dplyr::select(trial, hit, tr,time, cue_value, cue_value_num, voi, BOLD,recent_avg_gain,trial_gain, prediction_error_approx,recent_avg_winpercent,drift,last_gain,gain_contrast,last_iti,last_hit,last_cue)%>%
  filter(voi == "nacc")%>%
  mutate(tr = as.factor(tr),
         last_iti = as.factor(last_iti))

lm_nacc_iti <- lmer(BOLD ~ last_iti * tr * last_gain + (1|subject),nacc_iti_mod)

plot_model(lm_nacc_iti, type = "pred", terms = c("tr","last_iti","last_gain"),colors = purpleOrange_palette3)+
  geom_line()+
  theme_classic()+
  annotate("rect", xmin = 1, xmax = 2, ymin = -0.6, ymax = 0.5, 
           alpha = .2)+
  labs(title = "Nacc response by last gain and last iti")

lm_nacc_iti_earn5 <- lmer(BOLD ~ last_iti * tr * last_hit + cue_value * tr + (1|subject),nacc_iti_mod%>%filter(last_cue == "+$5"))
plot_model(lm_nacc_iti_earn5, type = "pred", terms = c("tr","last_hit","last_iti"),colors = purpleOrange_palette2)+
  geom_line()+
  theme_classic()+
  annotate("rect", xmin = 1, xmax = 2, ymin = -0.6, ymax = 0.5, 
           alpha = .2)+
  geom_hline(yintercept = 0, linetype = "dashed")+
  labs(title = "Nacc response by last hit and last iti (last cue +$5)")
```

```{r}
iti_mod <- tc_multimid_mb1%>%
  dplyr::select(trial, hit, tr,time, cue_value, cue_value_num, voi, BOLD,recent_avg_gain,trial_gain, prediction_error_approx,recent_avg_winpercent,drift,last_gain,gain_contrast,last_iti,last_hit, last_cue)%>%
  mutate(tr = as.factor(tr))

lm_iti5 <- lmer(BOLD ~ last_iti * tr * voi + (1|subject),iti_mod%>%filter(cue_value == "+$5"))

plot_model(lm_iti5, type = "pred", terms = c("tr","last_iti","voi"),colors = purpleOrange_palette3)+
  geom_hline(yintercept = 0)+
  geom_line()+
  annotate("rect", xmin = 1, xmax = 2, ymin = -0.6, ymax = 0.5, 
           alpha = .2)+
  labs(title = "Brain response collapsed at cue +$5")

lm_iti_5 <- lmer(BOLD ~ last_iti * tr * voi + (1|subject),iti_mod%>%filter(cue_value == "-$5"))

plot_model(lm_iti_5, type = "pred", terms = c("tr","last_iti","voi"),colors = purpleOrange_palette3)+
  geom_hline(yintercept = 0)+
  geom_line()+
  annotate("rect", xmin = 1, xmax = 2, ymin = -0.6, ymax = 0.5, 
           alpha = .2)+
  labs(title = "Brain response collapsed at cue -$5")

lm_iti_all <- lmer(BOLD ~ last_iti * tr * voi + (1|subject),iti_mod)

plot_model(lm_iti_all, type = "pred", terms = c("tr","last_iti","voi"),colors = purpleOrange_palette3)+
  geom_hline(yintercept = 0)+
  geom_line()+
  annotate("rect", xmin = 1, xmax = 2, ymin = -0.3, ymax = 0.3, 
           alpha = .2)+
  labs(title = "Brain response collapsed across all cues")

lm_iti_tr1 <- lmer(BOLD ~ last_iti * voi * last_gain + (1|subject),iti_mod%>%filter(tr == 1))
summary(lm_iti_tr1)

plot_model(lm_iti_tr1, type = "pred", terms = c("last_gain","last_iti","voi"),colors = purpleOrange_palette3)+
  geom_hline(yintercept = 0)+
  geom_line()
```

## last gain * iti
```{r}
lm_nacc_iti_gain_tr1 <- lmer(BOLD ~ last_iti * last_cue * last_hit + cue_value + (1|subject),iti_mod%>%filter(tr == 1,voi == "nacc"))
plot_model(lm_nacc_iti_gain_tr1, type = "pred", terms = c("last_iti","last_hit","last_cue"),colors = purpleOrange_palette2)+
  geom_line()+
  labs(title = "Nacc response influenced by last trial's gain")
```
#intertrial correlated of BOLD signal
```{r}
df_time <- tc_multimid_mb1%>%
  dplyr::select(subject,trial, tr, BOLD, voi,last_iti, last_gain)%>%
  group_by(subject,voi)%>%
  pivot_wider(names_from = tr,values_from = BOLD, names_prefix = "BOLD_")%>%
  mutate_at(vars(BOLD_1:BOLD_10), list(lag = ~ lag(.x, 1)))%>%
  mutate_at(vars(BOLD_1_lag:BOLD_10_lag), list(`2` = ~ lag(.x, 1)))%>%
  mutate_at(vars(BOLD_1_lag_2:BOLD_10_lag_2), list(`3` = ~ lag(.x, 1)))%>%
  mutate_at(vars(BOLD_1_lag_2_3:BOLD_10_lag_2_3), list(`4` = ~ lag(.x, 1)))

names(df_time)

lm_time <- lmer(BOLD_1 ~ BOLD_8_lag * last_iti + (1|subject),df_time%>%filter(voi == "nacc"))
summary(lm_time)
plot_model(lm_time, type = "pred", terms = c("BOLD_8_lag","last_iti"), show.data = TRUE)

lm_time2 <- lmer(BOLD_1 ~ BOLD_8_lag * last_iti * voi + (1|subject),df_time)
summary(lm_time2)
plot_model(lm_time2, type = "pred", terms = c("BOLD_8_lag","last_iti","voi"), show.data = TRUE)
```